---
title: |
  | MATH 4502 - Statistics for Process Control
  | Homework 3 - Modeling Process Quality
author: "Pranav Singh"
date: "01/24/2017"
output: pdf_document
ouptut:
  pdf_document:
    toc: yes
toc_depth: 2
---
```{r setup}
library(knitr)
opts_chunk$set(cache = T)
```

```{r, include = F}
data.3.1 <- c(16.05, 16.03, 16.02, 16.04, 16.05, 16.01, 16.02, 16.02, 16.03, 16.01, 16.00, 16.07)
data.3.2 <- c(50.001, 50.002, 49.998, 50.006, 50.005, 49.996, 50.003, 50.004)

data.3.8 <- "127 124
125 123
131 120
124 119
129 128
121 133
142 137
151 124
160 142
125 123
121 118
136 131
140 125
137 133
125 141
124 125
128 140
129 131
130 129
122 126"
con.3.8 <- textConnection(data.3.8)
data.3.8 <- read.csv(con.3.8, sep = ' ')
colnames(data.3.8) <- c('Component', 'Failure.Time')

data.3.9 <- "94.1 87.3 94.1
93.2 84.1 92.1
90.6 90.1 96.4
91.4 95.2 88.2
88.2 86.1 86.4
86.1 94.3 85.0
95.1 93.2 84.9
90.0 86.7 87.3
92.4 83.0 89.6
87.3 95.3 90.3
86.6 94.1 93.1
91.2 97.8 94.6
86.1 93.1 96.3
90.4 86.4 94.7
89.1 87.6 91.1
92.4 84.6 85.4
90.6 83.6 86.6
89.1 85.4 91.7
88.8 89.7 87.5
86.4 87.6 84.2
85.1 85.1 85.1
84.0 89.6 90.5
93.7 90.0 95.6
87.7 90.1 88.3
90.6 94.3 84.1
89.4 97.3 83.7
88.6 96.8 82.9
84.1 94.4 87.3
82.6 96.1 86.4
83.1 98.0 84.5"
con.3.9 <- textConnection(data.3.9)
data.3.9 <- read.csv(con.3.9, sep = ' ')
data.3.9 <- as.data.frame(matrix(as.matrix(data.3.9), ncol = 1))
colnames(data.3.9) <- 'yield'
```


# 3.1 
```{r}
n <- length(data.3.1)
mean.sample <- sum(data.3.1) / n
print(paste0('Sample Average: ', mean.sample))

var.sample <- sum( (data.3.1 - mean.sample)^2 ) / (n-1)
sd.sample <- sqrt(var.sample)
print(paste0('Sample Standard Deviation: ', sd.sample))
```

# 3.2
```{r}
n <- length(data.3.2)
mean.sample <- sum(data.3.2) / n
print(paste0('Sample Average: ', mean.sample))

var.sample <- sum( (data.3.2 - mean.sample)^2 ) / (n-1)
sd.sample <- sqrt(var.sample)
print(paste0('Sample Standard Deviation: ', sd.sample))
```

# 3.8
```{r}
x <- data.3.8$Failure.Time
n <- length(x)
mean.sample <- sum(x) / n
print(paste0('Sample Average: ', mean.sample))

var.sample <- sum( (x - mean.sample)^2 ) / (n-1)
sd.sample <- sqrt(var.sample)
print(paste0('Sample Standard Deviation: ', sd.sample))

hist(x)
stem(x)

print(paste0('Sample median: ', quantile(x, .5)))
print(paste0('Sample lower quartile: ', quantile(x, .25)))
print(paste0('Sample lower upper: ', quantile(x, .75)))
```


# 3.9
```{r}
hist(data.3.9$yield, breaks = 'Scott')
```
The histogram's shape resembles a bimodal distribution formed as a mixture of two normal distributions with means of approximately 87 and 95.

# 3.13
```{r}
qqnorm(data.3.9$yield)
qqline(data.3.9$yield)
```
The normal probability plot above doesn't show any signficant or systematic deviations from the assumption that the failure time for the component follows a normal distribution. So the assumption seems reasonable.

# 3.25
```{r}
boxplot(data.3.1)
```

# 3.26
```{r}
boxplot(data.3.2)
```

# 3.29
```{r}
prob.1.defect <- ppois(1, .02) - ppois(0, .02) # a
prob.atleast.1.defects <- ppois(1, .02, lower.tail = F) # b
```
(c) Lowering the occurrence rate of defects will lower the probability that an assembly will have one or more defects.
```{r}
prob.atleast.1.defects <- ppois(1, .01, lower.tail = F) # c
```

# 3.34
```{r}
f <- function(x) { 
  if ((11.75 <= x) & (x <= 12.25))
    4*(x-11.75)
  else if ((12.25 < x) & (x <= 12.75)) 
    4*(12.75-x)
  else
    0
}
# Answer:
integrate(Vectorize(f), 11.75, 12)

# Verify it's a true probability distribution:  
integrate(Vectorize(f), 11.75, 12.75)
```

# 3.35
```{r}
prob.atleast.1.defect.per.sample <- 1 - (1-.01)^25
```

# 3.39
```{r}
prob.exactly.1.prediabetic <- .9^3 * (1-.9)^1
prob.none.prediabetic <- .9^4
prob.atleast.1.prediabetic <- 1 - prob.none.prediabetic 
```
The probability that exactly one of the four participants is prediabetic is `r prob.exactly.1.prediabetic`. The probability that at least one of the four participants is prediabetic is `r prob.atleast.1.prediabetic`.

# 3.44
```{r}
p <- 3 / 50
prob.exactly.1 <- p * (1-p)^4
prob.none <- (1-p)^5
prob.atleast.1 <- 1 - prob.none
```
The probability that the sample contains exactly one nonconforming unit is `r prob.exactly.1`. The probability that it contains at least one nonconforming unit is `r prob.atleast.1`.

# 3.46(Poisson)
```{r}
ppois(1, .1, lower.tail = F)
```

# 3.51
```{r}
n <- 50000
mu <- 40
sd <- 5
p.less.than.35 <- pnorm(35, mu, sd)
p.more.than.48 <- pnorm(48, mu, sd, lower.tail = F)

num.expected.less.than.35 <- n * p.less.than.35
num.expected.less.than.35
num.expected.more.than.48 <- n * p.more.than.48
num.expected.more.than.48
```

# 3.52
```{r}
mu <- 5
sd <- .02
pnorm(5.05, mu, sd) - pnorm(4.95, mu, sd)
```

